Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-26 paper/current/main.tex
fix affilation error

\affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
2300 AX Leiden, The Netherlands}
\affil{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
\affil[5]{Department of Physics, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[6]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}

>>>>

\affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
2300 AX Leiden, The Netherlands}
\affil[4]{DST-NRF Centre of Excellence in Scientometrics and Science, Technology and Innovation Policy, Stellenbosch University, Stellenbosch, South Africa}
\affil[5]{Department of Physics, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[6]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}
